---
title: "Gibbs Free Energy for Silica Glass Fiber Draws"
output: html_notebook
---

## Gibbs Free Energy Equation
### &nbsp;&nbsp;&nbsp;&nbsp; dG = dH(kJ/mol) - T*S(J/mol)*E-3
### &nbsp;&nbsp;&nbsp;&nbsp; dG = G(products) - G(reactants)
### &nbsp;&nbsp;&nbsp;&nbsp; if dG > 0, reaction will propagate backward
### &nbsp;&nbsp;&nbsp;&nbsp; if dG < 0, reaction will propogate forward

## Schomate Equation
### &nbsp;&nbsp;&nbsp;&nbsp; dH(kJ/mol) = A*t + (B*t^2)/2 + (C*t^3)/3 + (D*t^4)/4 - E/t + F - H
### &nbsp;&nbsp;&nbsp;&nbsp; S(J/mol) = A*ln(t) + B*t + (C*t^2)/2 + (D*t^3)/3 - E/(2*t^2) + G
#### &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; t = T/1000

### Upload libraries
```{r}
library(ggplot2)
library(readxl)
```

### Upload dataset and grab relevant data
```{r}
dataset <- read_excel('ThermodynamicPropertiesData.xlsx')

dataGibbs <- dataset[-c(24:29, 40:52), ]
```

### Create temperature array
```{r}
lowTemp <- 293
maxTemp <- 2600
T <- c(lowTemp:maxTemp)
t <- T/1000
```

### Create enthalpy arrays for respective coefficients and temperature ranges
#### dH(kJ/mol) = A*t + (B*t^2)/2 + (C*t^3)/3 + (D*t^4)/4 - E/t + F - H + H293
```{r}
H_O2 <- c(dataGibbs$A[1]*t[match(c(lowTemp:dataGibbs$Max_Temp[1]), T)] +
          (dataGibbs$B[1]*t[match(c(lowTemp:dataGibbs$Max_Temp[1]), T)]^2)/2 +
          (dataGibbs$C[1]*t[match(c(lowTemp:dataGibbs$Max_Temp[1]), T)]^3)/3 +
          (dataGibbs$D[1]*t[match(c(lowTemp:dataGibbs$Max_Temp[1]), T)]^4)/4 -
          dataGibbs$E[1]/t[match(c(lowTemp:dataGibbs$Max_Temp[1]), T)] + 
          dataGibbs$F[1] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[1] - dataGibbs$H[1], 
        dataGibbs$A[2]*t[match(c((dataGibbs$Max_Temp[1]+1):dataGibbs$Max_Temp[2]),T)] +
          (dataGibbs$B[2]*t[match(c((dataGibbs$Max_Temp[1]+1):dataGibbs$Max_Temp[2]),T)]^2)/2 +
          (dataGibbs$C[2]*t[match(c((dataGibbs$Max_Temp[1]+1):dataGibbs$Max_Temp[2]),T)]^3)/3 +
          (dataGibbs$D[2]*t[match(c((dataGibbs$Max_Temp[1]+1):dataGibbs$Max_Temp[2]),T)]^4)/4 -
          dataGibbs$E[2]/t[match(c((dataGibbs$Max_Temp[1]+1):dataGibbs$Max_Temp[2]),T)] + 
          dataGibbs$F[2] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[2] - dataGibbs$H[2],
        dataGibbs$A[3]*t[match(c((dataGibbs$Max_Temp[2]+1):maxTemp), T)] +
          (dataGibbs$B[3]*t[match(c((dataGibbs$Max_Temp[2]+1):maxTemp), T)]^2)/2 +
          (dataGibbs$C[3]*t[match(c((dataGibbs$Max_Temp[2]+1):maxTemp), T)]^3)/3 +
          (dataGibbs$D[3]*t[match(c((dataGibbs$Max_Temp[2]+1):maxTemp), T)]^4)/4 -
          dataGibbs$E[3]/t[match(c((dataGibbs$Max_Temp[2]+1):maxTemp), T)] + 
          dataGibbs$F[3] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[3] - dataGibbs$H[3])

H_Si <- c(dataGibbs$A[4]*t[match(c(lowTemp:dataGibbs$Max_Temp[4]), T)] +
          (dataGibbs$B[4]*t[match(c(lowTemp:dataGibbs$Max_Temp[4]), T)]^2)/2 +
          (dataGibbs$C[4]*t[match(c(lowTemp:dataGibbs$Max_Temp[4]), T)]^3)/3 +
          (dataGibbs$D[4]*t[match(c(lowTemp:dataGibbs$Max_Temp[4]), T)]^4)/4 -
          dataGibbs$E[4]/t[match(c(lowTemp:dataGibbs$Max_Temp[4]), T)] + 
          dataGibbs$F[4] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[4] - dataGibbs$H[4], 
        dataGibbs$A[5]*t[match(c((dataGibbs$Max_Temp[4]+1):maxTemp),T)] +
          (dataGibbs$B[5]*t[match(c((dataGibbs$Max_Temp[4]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[5]*t[match(c((dataGibbs$Max_Temp[4]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[5]*t[match(c((dataGibbs$Max_Temp[4]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[5]/t[match(c((dataGibbs$Max_Temp[4]+1):maxTemp),T)] + 
          dataGibbs$F[5] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[5] - dataGibbs$H[5])

H_SiO2 <- c(dataGibbs$A[6]*t[match(c(lowTemp:dataGibbs$Max_Temp[6]), T)] +
          (dataGibbs$B[6]*t[match(c(lowTemp:dataGibbs$Max_Temp[6]), T)]^2)/2 +
          (dataGibbs$C[6]*t[match(c(lowTemp:dataGibbs$Max_Temp[6]), T)]^3)/3 +
          (dataGibbs$D[6]*t[match(c(lowTemp:dataGibbs$Max_Temp[6]), T)]^4)/4 -
          dataGibbs$E[6]/t[match(c(lowTemp:dataGibbs$Max_Temp[6]), T)] + 
          dataGibbs$F[6] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[6] - dataGibbs$H[6], 
        dataGibbs$A[7]*t[match(c((dataGibbs$Max_Temp[6]+1):dataGibbs$Max_Temp[7]),T)] +
          (dataGibbs$B[7]*t[match(c((dataGibbs$Max_Temp[6]+1):dataGibbs$Max_Temp[7]),T)]^2)/2 +
          (dataGibbs$C[7]*t[match(c((dataGibbs$Max_Temp[6]+1):dataGibbs$Max_Temp[7]),T)]^3)/3 +
          (dataGibbs$D[7]*t[match(c((dataGibbs$Max_Temp[6]+1):dataGibbs$Max_Temp[7]),T)]^4)/4 -
          dataGibbs$E[7]/t[match(c((dataGibbs$Max_Temp[6]+1):dataGibbs$Max_Temp[7]),T)] + 
          dataGibbs$F[7] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[7] - dataGibbs$H[7],
        dataGibbs$A[8]*t[match(c((dataGibbs$Max_Temp[7]+1):maxTemp), T)] +
          (dataGibbs$B[8]*t[match(c((dataGibbs$Max_Temp[7]+1):maxTemp), T)]^2)/2 +
          (dataGibbs$C[8]*t[match(c((dataGibbs$Max_Temp[7]+1):maxTemp), T)]^3)/3 +
          (dataGibbs$D[8]*t[match(c((dataGibbs$Max_Temp[7]+1):maxTemp), T)]^4)/4 -
          dataGibbs$E[8]/t[match(c((dataGibbs$Max_Temp[7]+1):maxTemp), T)] + 
          dataGibbs$F[8] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[8] - dataGibbs$H[8])

H_Al <- c(dataGibbs$A[9]*t[match(c(lowTemp:dataGibbs$Max_Temp[9]), T)] +
          (dataGibbs$B[9]*t[match(c(lowTemp:dataGibbs$Max_Temp[9]), T)]^2)/2 +
          (dataGibbs$C[9]*t[match(c(lowTemp:dataGibbs$Max_Temp[9]), T)]^3)/3 +
          (dataGibbs$D[9]*t[match(c(lowTemp:dataGibbs$Max_Temp[9]), T)]^4)/4 -
          dataGibbs$E[9]/t[match(c(lowTemp:dataGibbs$Max_Temp[9]), T)] + 
          dataGibbs$F[9] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[9] - dataGibbs$H[9], 
        dataGibbs$A[10]*t[match(c((dataGibbs$Max_Temp[9]+1):maxTemp),T)] +
          (dataGibbs$B[10]*t[match(c((dataGibbs$Max_Temp[9]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[10]*t[match(c((dataGibbs$Max_Temp[9]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[10]*t[match(c((dataGibbs$Max_Temp[9]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[10]/t[match(c((dataGibbs$Max_Temp[9]+1):maxTemp),T)] + 
          dataGibbs$F[10] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[10] - dataGibbs$H[10])

H_Al2O3_alpha <- c(dataGibbs$A[11]*t[match(c(lowTemp:dataGibbs$Max_Temp[11]), T)] +
          (dataGibbs$B[11]*t[match(c(lowTemp:dataGibbs$Max_Temp[11]), T)]^2)/2 +
          (dataGibbs$C[11]*t[match(c(lowTemp:dataGibbs$Max_Temp[11]), T)]^3)/3 +
          (dataGibbs$D[11]*t[match(c(lowTemp:dataGibbs$Max_Temp[11]), T)]^4)/4 -
          dataGibbs$E[11]/t[match(c(lowTemp:dataGibbs$Max_Temp[11]), T)] + 
          dataGibbs$F[11] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[11] - dataGibbs$H[11], 
        dataGibbs$A[15]*t[match(c((dataGibbs$Max_Temp[11]+1):maxTemp),T)] +
          (dataGibbs$B[15]*t[match(c((dataGibbs$Max_Temp[11]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[15]*t[match(c((dataGibbs$Max_Temp[11]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[15]*t[match(c((dataGibbs$Max_Temp[11]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[15]/t[match(c((dataGibbs$Max_Temp[11]+1):maxTemp),T)] + 
          dataGibbs$F[15] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[15] - dataGibbs$H[15])

H_Al2O3_gamma <- c(dataGibbs$A[12]*t[match(c(lowTemp:dataGibbs$Max_Temp[12]), T)] +
          (dataGibbs$B[12]*t[match(c(lowTemp:dataGibbs$Max_Temp[12]), T)]^2)/2 +
          (dataGibbs$C[12]*t[match(c(lowTemp:dataGibbs$Max_Temp[12]), T)]^3)/3 +
          (dataGibbs$D[12]*t[match(c(lowTemp:dataGibbs$Max_Temp[12]), T)]^4)/4 -
          dataGibbs$E[12]/t[match(c(lowTemp:dataGibbs$Max_Temp[12]), T)] + 
          dataGibbs$F[12] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[12] - dataGibbs$H[12], 
        dataGibbs$A[15]*t[match(c((dataGibbs$Max_Temp[12]+1):maxTemp),T)] +
          (dataGibbs$B[15]*t[match(c((dataGibbs$Max_Temp[12]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[15]*t[match(c((dataGibbs$Max_Temp[12]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[15]*t[match(c((dataGibbs$Max_Temp[12]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[15]/t[match(c((dataGibbs$Max_Temp[12]+1):maxTemp),T)] + 
          dataGibbs$F[15] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[15] - dataGibbs$H[15])

H_Al2O3_delta <- c(dataGibbs$A[13]*t[match(c(lowTemp:dataGibbs$Max_Temp[13]), T)] +
          (dataGibbs$B[13]*t[match(c(lowTemp:dataGibbs$Max_Temp[13]), T)]^2)/2 +
          (dataGibbs$C[13]*t[match(c(lowTemp:dataGibbs$Max_Temp[13]), T)]^3)/3 +
          (dataGibbs$D[13]*t[match(c(lowTemp:dataGibbs$Max_Temp[13]), T)]^4)/4 -
          dataGibbs$E[13]/t[match(c(lowTemp:dataGibbs$Max_Temp[13]), T)] + 
          dataGibbs$F[13] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[13] - dataGibbs$H[13], 
        dataGibbs$A[15]*t[match(c((dataGibbs$Max_Temp[13]+1):maxTemp),T)] +
          (dataGibbs$B[15]*t[match(c((dataGibbs$Max_Temp[13]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[15]*t[match(c((dataGibbs$Max_Temp[13]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[15]*t[match(c((dataGibbs$Max_Temp[13]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[15]/t[match(c((dataGibbs$Max_Temp[13]+1):maxTemp),T)] + 
          dataGibbs$F[15] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[15] - dataGibbs$H[15])

H_Al2O3_kappa <- c(dataGibbs$A[14]*t[match(c(lowTemp:dataGibbs$Max_Temp[14]), T)] +
          (dataGibbs$B[14]*t[match(c(lowTemp:dataGibbs$Max_Temp[14]), T)]^2)/2 +
          (dataGibbs$C[14]*t[match(c(lowTemp:dataGibbs$Max_Temp[14]), T)]^3)/3 +
          (dataGibbs$D[14]*t[match(c(lowTemp:dataGibbs$Max_Temp[14]), T)]^4)/4 -
          dataGibbs$E[14]/t[match(c(lowTemp:dataGibbs$Max_Temp[14]), T)] + 
          dataGibbs$F[14] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[14] - dataGibbs$H[14], 
        dataGibbs$A[15]*t[match(c((dataGibbs$Max_Temp[14]+1):maxTemp),T)] +
          (dataGibbs$B[15]*t[match(c((dataGibbs$Max_Temp[14]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[15]*t[match(c((dataGibbs$Max_Temp[14]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[15]*t[match(c((dataGibbs$Max_Temp[14]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[15]/t[match(c((dataGibbs$Max_Temp[14]+1):maxTemp),T)] + 
          dataGibbs$F[15] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[15] - dataGibbs$H[15])

H_V <- c(dataGibbs$A[16]*t[match(c(lowTemp:dataGibbs$Max_Temp[16]), T)] +
          (dataGibbs$B[16]*t[match(c(lowTemp:dataGibbs$Max_Temp[16]), T)]^2)/2 +
          (dataGibbs$C[16]*t[match(c(lowTemp:dataGibbs$Max_Temp[16]), T)]^3)/3 +
          (dataGibbs$D[16]*t[match(c(lowTemp:dataGibbs$Max_Temp[16]), T)]^4)/4 -
          dataGibbs$E[16]/t[match(c(lowTemp:dataGibbs$Max_Temp[16]), T)] + 
          dataGibbs$F[16] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[16] - dataGibbs$H[16], 
        dataGibbs$A[17]*t[match(c((dataGibbs$Max_Temp[16]+1):maxTemp),T)] +
          (dataGibbs$B[17]*t[match(c((dataGibbs$Max_Temp[16]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[17]*t[match(c((dataGibbs$Max_Temp[16]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[17]*t[match(c((dataGibbs$Max_Temp[16]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[17]/t[match(c((dataGibbs$Max_Temp[16]+1):maxTemp),T)] + 
          dataGibbs$F[17] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[17] - dataGibbs$H[17])

H_VO <- c(dataGibbs$A[18]*t[match(c(lowTemp:dataGibbs$Max_Temp[18]), T)] +
          (dataGibbs$B[18]*t[match(c(lowTemp:dataGibbs$Max_Temp[18]), T)]^2)/2 +
          (dataGibbs$C[18]*t[match(c(lowTemp:dataGibbs$Max_Temp[18]), T)]^3)/3 +
          (dataGibbs$D[18]*t[match(c(lowTemp:dataGibbs$Max_Temp[18]), T)]^4)/4 -
          dataGibbs$E[18]/t[match(c(lowTemp:dataGibbs$Max_Temp[18]), T)] + 
          dataGibbs$F[18] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[18] - dataGibbs$H[18], 
        dataGibbs$A[19]*t[match(c((dataGibbs$Max_Temp[18]+1):maxTemp),T)] +
          (dataGibbs$B[19]*t[match(c((dataGibbs$Max_Temp[18]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[19]*t[match(c((dataGibbs$Max_Temp[18]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[19]*t[match(c((dataGibbs$Max_Temp[18]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[19]/t[match(c((dataGibbs$Max_Temp[18]+1):maxTemp),T)] + 
          dataGibbs$F[19] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[19] - dataGibbs$H[19])

H_V2O3 <- c(dataGibbs$A[20]*t[match(c(lowTemp:dataGibbs$Max_Temp[20]), T)] +
          (dataGibbs$B[20]*t[match(c(lowTemp:dataGibbs$Max_Temp[20]), T)]^2)/2 +
          (dataGibbs$C[20]*t[match(c(lowTemp:dataGibbs$Max_Temp[20]), T)]^3)/3 +
          (dataGibbs$D[20]*t[match(c(lowTemp:dataGibbs$Max_Temp[20]), T)]^4)/4 -
          dataGibbs$E[20]/t[match(c(lowTemp:dataGibbs$Max_Temp[20]), T)] + 
          dataGibbs$F[20] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[20] - dataGibbs$H[20], 
        dataGibbs$A[21]*t[match(c((dataGibbs$Max_Temp[20]+1):maxTemp),T)] +
          (dataGibbs$B[21]*t[match(c((dataGibbs$Max_Temp[20]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[21]*t[match(c((dataGibbs$Max_Temp[20]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[21]*t[match(c((dataGibbs$Max_Temp[20]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[21]/t[match(c((dataGibbs$Max_Temp[20]+1):maxTemp),T)] + 
          dataGibbs$F[21] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[21] - dataGibbs$H[21])

H_V2O5 <- c(dataGibbs$A[22]*t[match(c(lowTemp:dataGibbs$Max_Temp[22]), T)] +
          (dataGibbs$B[22]*t[match(c(lowTemp:dataGibbs$Max_Temp[22]), T)]^2)/2 +
          (dataGibbs$C[22]*t[match(c(lowTemp:dataGibbs$Max_Temp[22]), T)]^3)/3 +
          (dataGibbs$D[22]*t[match(c(lowTemp:dataGibbs$Max_Temp[22]), T)]^4)/4 -
          dataGibbs$E[22]/t[match(c(lowTemp:dataGibbs$Max_Temp[22]), T)] + 
          dataGibbs$F[22] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[22] - dataGibbs$H[22], 
        dataGibbs$A[23]*t[match(c((dataGibbs$Max_Temp[22]+1):maxTemp),T)] +
          (dataGibbs$B[23]*t[match(c((dataGibbs$Max_Temp[22]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[23]*t[match(c((dataGibbs$Max_Temp[22]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[23]*t[match(c((dataGibbs$Max_Temp[22]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[23]/t[match(c((dataGibbs$Max_Temp[22]+1):maxTemp),T)] + 
          dataGibbs$F[23] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[23] - dataGibbs$H[23])

H_Ti_alpha <- c(dataGibbs$A[24]*t[match(c(lowTemp:dataGibbs$Max_Temp[24]), T)] +
          (dataGibbs$B[24]*t[match(c(lowTemp:dataGibbs$Max_Temp[24]), T)]^2)/2 +
          (dataGibbs$C[24]*t[match(c(lowTemp:dataGibbs$Max_Temp[24]), T)]^3)/3 +
          (dataGibbs$D[24]*t[match(c(lowTemp:dataGibbs$Max_Temp[24]), T)]^4)/4 -
          dataGibbs$E[24]/t[match(c(lowTemp:dataGibbs$Max_Temp[24]), T)] + 
          dataGibbs$F[24] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[24] - dataGibbs$H[24], 
        dataGibbs$A[25]*t[match(c((dataGibbs$Max_Temp[24]+1):dataGibbs$Max_Temp[25]),T)] +
          (dataGibbs$B[25]*t[match(c((dataGibbs$Max_Temp[24]+1):dataGibbs$Max_Temp[25]),T)]^2)/2 +
          (dataGibbs$C[25]*t[match(c((dataGibbs$Max_Temp[24]+1):dataGibbs$Max_Temp[25]),T)]^3)/3 +
          (dataGibbs$D[25]*t[match(c((dataGibbs$Max_Temp[24]+1):dataGibbs$Max_Temp[25]),T)]^4)/4 -
          dataGibbs$E[25]/t[match(c((dataGibbs$Max_Temp[24]+1):dataGibbs$Max_Temp[25]),T)] + 
          dataGibbs$F[25] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[25] - dataGibbs$H[25],
        dataGibbs$A[27]*t[match(c((dataGibbs$Max_Temp[25]+1):maxTemp), T)] +
          (dataGibbs$B[27]*t[match(c((dataGibbs$Max_Temp[25]+1):maxTemp), T)]^2)/2 +
          (dataGibbs$C[27]*t[match(c((dataGibbs$Max_Temp[25]+1):maxTemp), T)]^3)/3 +
          (dataGibbs$D[27]*t[match(c((dataGibbs$Max_Temp[25]+1):maxTemp), T)]^4)/4 -
          dataGibbs$E[27]/t[match(c((dataGibbs$Max_Temp[25]+1):maxTemp), T)] + 
          dataGibbs$F[27] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[27] - dataGibbs$H[27])

H_Ti_beta <- c(dataGibbs$A[26]*t[match(c(lowTemp:dataGibbs$Max_Temp[26]), T)] +
          (dataGibbs$B[26]*t[match(c(lowTemp:dataGibbs$Max_Temp[26]), T)]^2)/2 +
          (dataGibbs$C[26]*t[match(c(lowTemp:dataGibbs$Max_Temp[26]), T)]^3)/3 +
          (dataGibbs$D[26]*t[match(c(lowTemp:dataGibbs$Max_Temp[26]), T)]^4)/4 -
          dataGibbs$E[26]/t[match(c(lowTemp:dataGibbs$Max_Temp[26]), T)] + 
          dataGibbs$F[26] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[26] - dataGibbs$H[26], 
        dataGibbs$A[27]*t[match(c((dataGibbs$Max_Temp[26]+1):maxTemp),T)] +
          (dataGibbs$B[27]*t[match(c((dataGibbs$Max_Temp[26]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[27]*t[match(c((dataGibbs$Max_Temp[26]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[27]*t[match(c((dataGibbs$Max_Temp[26]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[27]/t[match(c((dataGibbs$Max_Temp[26]+1):maxTemp),T)] + 
          dataGibbs$F[27] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[27] - dataGibbs$H[27])

H_Ti2O3 <- c(dataGibbs$A[28]*t[match(c(lowTemp:dataGibbs$Max_Temp[28]), T)] +
          (dataGibbs$B[28]*t[match(c(lowTemp:dataGibbs$Max_Temp[28]), T)]^2)/2 +
          (dataGibbs$C[28]*t[match(c(lowTemp:dataGibbs$Max_Temp[28]), T)]^3)/3 +
          (dataGibbs$D[28]*t[match(c(lowTemp:dataGibbs$Max_Temp[28]), T)]^4)/4 -
          dataGibbs$E[28]/t[match(c(lowTemp:dataGibbs$Max_Temp[28]), T)] + 
          dataGibbs$F[28] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[28] - dataGibbs$H[28], 
        dataGibbs$A[29]*t[match(c((dataGibbs$Max_Temp[28]+1):dataGibbs$Max_Temp[29]),T)] +
          (dataGibbs$B[29]*t[match(c((dataGibbs$Max_Temp[28]+1):dataGibbs$Max_Temp[29]),T)]^2)/2 +
          (dataGibbs$C[29]*t[match(c((dataGibbs$Max_Temp[28]+1):dataGibbs$Max_Temp[29]),T)]^3)/3 +
          (dataGibbs$D[29]*t[match(c((dataGibbs$Max_Temp[28]+1):dataGibbs$Max_Temp[29]),T)]^4)/4 -
          dataGibbs$E[29]/t[match(c((dataGibbs$Max_Temp[28]+1):dataGibbs$Max_Temp[29]),T)] + 
          dataGibbs$F[29] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[29] - dataGibbs$H[29],
        dataGibbs$A[30]*t[match(c((dataGibbs$Max_Temp[29]+1):maxTemp), T)] +
          (dataGibbs$B[30]*t[match(c((dataGibbs$Max_Temp[29]+1):maxTemp), T)]^2)/2 +
          (dataGibbs$C[30]*t[match(c((dataGibbs$Max_Temp[29]+1):maxTemp), T)]^3)/3 +
          (dataGibbs$D[30]*t[match(c((dataGibbs$Max_Temp[29]+1):maxTemp), T)]^4)/4 -
          dataGibbs$E[30]/t[match(c((dataGibbs$Max_Temp[29]+1):maxTemp), T)] + 
          dataGibbs$F[30] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[30] - dataGibbs$H[30])

H_TiO_alpha <- c(dataGibbs$A[31]*t[match(c(lowTemp:dataGibbs$Max_Temp[31]), T)] +
          (dataGibbs$B[31]*t[match(c(lowTemp:dataGibbs$Max_Temp[31]), T)]^2)/2 +
          (dataGibbs$C[31]*t[match(c(lowTemp:dataGibbs$Max_Temp[31]), T)]^3)/3 +
          (dataGibbs$D[31]*t[match(c(lowTemp:dataGibbs$Max_Temp[31]), T)]^4)/4 -
          dataGibbs$E[31]/t[match(c(lowTemp:dataGibbs$Max_Temp[31]), T)] + 
          dataGibbs$F[31] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[31] - dataGibbs$H[31], 
        dataGibbs$A[33]*t[match(c((dataGibbs$Max_Temp[31]+1):maxTemp),T)] +
          (dataGibbs$B[33]*t[match(c((dataGibbs$Max_Temp[31]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[33]*t[match(c((dataGibbs$Max_Temp[31]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[33]*t[match(c((dataGibbs$Max_Temp[31]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[33]/t[match(c((dataGibbs$Max_Temp[31]+1):maxTemp),T)] + 
          dataGibbs$F[33] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[33] - dataGibbs$H[33])

H_TiO_beta <- c(dataGibbs$A[32]*t[match(c(lowTemp:dataGibbs$Max_Temp[32]), T)] +
          (dataGibbs$B[32]*t[match(c(lowTemp:dataGibbs$Max_Temp[32]), T)]^2)/2 +
          (dataGibbs$C[32]*t[match(c(lowTemp:dataGibbs$Max_Temp[32]), T)]^3)/3 +
          (dataGibbs$D[32]*t[match(c(lowTemp:dataGibbs$Max_Temp[32]), T)]^4)/4 -
          dataGibbs$E[32]/t[match(c(lowTemp:dataGibbs$Max_Temp[32]), T)] + 
          dataGibbs$F[32]  + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[32] - dataGibbs$H[32], 
        dataGibbs$A[33]*t[match(c((dataGibbs$Max_Temp[32]+1):maxTemp),T)] +
          (dataGibbs$B[33]*t[match(c((dataGibbs$Max_Temp[32]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[33]*t[match(c((dataGibbs$Max_Temp[32]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[33]*t[match(c((dataGibbs$Max_Temp[32]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[33]/t[match(c((dataGibbs$Max_Temp[32]+1):maxTemp),T)] + 
          dataGibbs$F[33] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[33] - dataGibbs$H[33])

H_Cu <- c(dataGibbs$A[34]*t[match(c(lowTemp:dataGibbs$Max_Temp[34]), T)] +
          (dataGibbs$B[34]*t[match(c(lowTemp:dataGibbs$Max_Temp[34]), T)]^2)/2 +
          (dataGibbs$C[34]*t[match(c(lowTemp:dataGibbs$Max_Temp[34]), T)]^3)/3 +
          (dataGibbs$D[34]*t[match(c(lowTemp:dataGibbs$Max_Temp[34]), T)]^4)/4 -
          dataGibbs$E[34]/t[match(c(lowTemp:dataGibbs$Max_Temp[34]), T)] + 
          dataGibbs$F[34] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[34] - dataGibbs$H[34], 
        dataGibbs$A[35]*t[match(c((dataGibbs$Max_Temp[34]+1):maxTemp),T)] +
          (dataGibbs$B[35]*t[match(c((dataGibbs$Max_Temp[34]+1):maxTemp),T)]^2)/2 +
          (dataGibbs$C[35]*t[match(c((dataGibbs$Max_Temp[34]+1):maxTemp),T)]^3)/3 +
          (dataGibbs$D[35]*t[match(c((dataGibbs$Max_Temp[34]+1):maxTemp),T)]^4)/4 -
          dataGibbs$E[35]/t[match(c((dataGibbs$Max_Temp[34]+1):maxTemp),T)] + 
          dataGibbs$F[35] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[35] - dataGibbs$H[35])

H_Cu2O <- c(dataGibbs$A[36]*t[match(c(lowTemp:dataGibbs$Max_Temp[36]), T)] +
          (dataGibbs$B[36]*t[match(c(lowTemp:dataGibbs$Max_Temp[36]), T)]^2)/2 +
          (dataGibbs$C[36]*t[match(c(lowTemp:dataGibbs$Max_Temp[36]), T)]^3)/3 +
          (dataGibbs$D[36]*t[match(c(lowTemp:dataGibbs$Max_Temp[36]), T)]^4)/4 -
          dataGibbs$E[36]/t[match(c(lowTemp:dataGibbs$Max_Temp[36]), T)] + 
          dataGibbs$F[36] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[36] - dataGibbs$H[36], 
        dataGibbs$A[37]*t[match(c((dataGibbs$Max_Temp[36]+1):dataGibbs$Max_Temp[37]),T)] +
          (dataGibbs$B[37]*t[match(c((dataGibbs$Max_Temp[36]+1):dataGibbs$Max_Temp[37]),T)]^2)/2 +
          (dataGibbs$C[37]*t[match(c((dataGibbs$Max_Temp[36]+1):dataGibbs$Max_Temp[37]),T)]^3)/3 +
          (dataGibbs$D[37]*t[match(c((dataGibbs$Max_Temp[36]+1):dataGibbs$Max_Temp[37]),T)]^4)/4 -
          dataGibbs$E[37]/t[match(c((dataGibbs$Max_Temp[36]+1):dataGibbs$Max_Temp[37]),T)] + 
          dataGibbs$F[37] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[37] - dataGibbs$H[37],
        dataGibbs$A[38]*t[match(c((dataGibbs$Max_Temp[37]+1):maxTemp), T)] +
          (dataGibbs$B[38]*t[match(c((dataGibbs$Max_Temp[37]+1):maxTemp), T)]^2)/2 +
          (dataGibbs$C[38]*t[match(c((dataGibbs$Max_Temp[37]+1):maxTemp), T)]^3)/3 +
          (dataGibbs$D[38]*t[match(c((dataGibbs$Max_Temp[37]+1):maxTemp), T)]^4)/4 -
          dataGibbs$E[38]/t[match(c((dataGibbs$Max_Temp[37]+1):maxTemp), T)] + 
          dataGibbs$F[38] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[38] - dataGibbs$H[38])

H_CuO <- c(dataGibbs$A[39]*t[match(c(lowTemp:maxTemp), T)] +
          (dataGibbs$B[39]*t[match(c(lowTemp:maxTemp), T)]^2)/2 +
          (dataGibbs$C[39]*t[match(c(lowTemp:maxTemp), T)]^3)/3 +
          (dataGibbs$D[39]*t[match(c(lowTemp:maxTemp), T)]^4)/4 -
          dataGibbs$E[39]/t[match(c(lowTemp:maxTemp), T)] + 
          dataGibbs$F[39] + dataGibbs$`Enthalpy of Formation (H298) kJ/mol`[39] - dataGibbs$H[39])
```


### Create entropy arrays for respective coefficients and temperature ranges
#### S(J/mol) = A*ln(t) + B*t + (C*t^2)/2 + (D*t^3)/3 - E/(2*t^2) + G
```{r}
S_O2 <- c(dataGibbs$A[1]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[1]), T)]) +
            dataGibbs$B[1]*t[match(c(lowTemp:dataGibbs$Max_Temp[1]), T)] +
            (dataGibbs$C[1]*t[match(c(lowTemp:dataGibbs$Max_Temp[1]), T)]^2)/2 +
            (dataGibbs$D[1]*t[match(c(lowTemp:dataGibbs$Max_Temp[1]), T)]^3)/3 -
            dataGibbs$E[1]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[1]), T)]^2) +
            dataGibbs$G[1],
          dataGibbs$A[2]*log(t[match(c((dataGibbs$Max_Temp[1]+1):dataGibbs$Max_Temp[2]), T)]) +
            dataGibbs$B[2]*t[match(c((dataGibbs$Max_Temp[1]+1):dataGibbs$Max_Temp[2]), T)] +
            (dataGibbs$C[2]*t[match(c((dataGibbs$Max_Temp[1]+1):dataGibbs$Max_Temp[2]), T)]^2)/2 +
            (dataGibbs$D[2]*t[match(c((dataGibbs$Max_Temp[1]+1):dataGibbs$Max_Temp[2]), T)]^3)/3 -
            dataGibbs$E[2]/(2*t[match(c((dataGibbs$Max_Temp[1]+1):dataGibbs$Max_Temp[2]), T)]^2) +
            dataGibbs$G[2],
          dataGibbs$A[3]*log(t[match(c((dataGibbs$Max_Temp[2]+1):maxTemp), T)]) +
            dataGibbs$B[3]*t[match(c((dataGibbs$Max_Temp[2]+1):maxTemp), T)] +
            (dataGibbs$C[3]*t[match(c((dataGibbs$Max_Temp[2]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[3]*t[match(c((dataGibbs$Max_Temp[2]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[3]/(2*t[match(c((dataGibbs$Max_Temp[2]+1):maxTemp), T)]^2) +
            dataGibbs$G[3])

S_Si <- c(dataGibbs$A[4]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[4]), T)]) +
            dataGibbs$B[4]*t[match(c(lowTemp:dataGibbs$Max_Temp[4]), T)] +
            (dataGibbs$C[4]*t[match(c(lowTemp:dataGibbs$Max_Temp[4]), T)]^2)/2 +
            (dataGibbs$D[4]*t[match(c(lowTemp:dataGibbs$Max_Temp[4]), T)]^3)/3 -
            dataGibbs$E[4]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[4]), T)]^2) +
            dataGibbs$G[4],
          dataGibbs$A[5]*log(t[match(c((dataGibbs$Max_Temp[4]+1):maxTemp), T)]) +
            dataGibbs$B[5]*t[match(c((dataGibbs$Max_Temp[4]+1):maxTemp), T)] +
            (dataGibbs$C[5]*t[match(c((dataGibbs$Max_Temp[4]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[5]*t[match(c((dataGibbs$Max_Temp[4]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[5]/(2*t[match(c((dataGibbs$Max_Temp[4]+1):maxTemp), T)]^2) +
            dataGibbs$G[5])

S_SiO2 <- c(dataGibbs$A[6]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[6]), T)]) +
            dataGibbs$B[6]*t[match(c(lowTemp:dataGibbs$Max_Temp[6]), T)] +
            (dataGibbs$C[6]*t[match(c(lowTemp:dataGibbs$Max_Temp[6]), T)]^2)/2 +
            (dataGibbs$D[6]*t[match(c(lowTemp:dataGibbs$Max_Temp[6]), T)]^3)/3 -
            dataGibbs$E[6]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[6]), T)]^2) +
            dataGibbs$G[6],
          dataGibbs$A[7]*log(t[match(c((dataGibbs$Max_Temp[6]+1):dataGibbs$Max_Temp[7]), T)]) +
            dataGibbs$B[7]*t[match(c((dataGibbs$Max_Temp[6]+1):dataGibbs$Max_Temp[7]), T)] +
            (dataGibbs$C[7]*t[match(c((dataGibbs$Max_Temp[6]+1):dataGibbs$Max_Temp[7]), T)]^2)/2 +
            (dataGibbs$D[7]*t[match(c((dataGibbs$Max_Temp[6]+1):dataGibbs$Max_Temp[7]), T)]^3)/3 -
            dataGibbs$E[7]/(2*t[match(c((dataGibbs$Max_Temp[6]+1):dataGibbs$Max_Temp[7]), T)]^2) +
            dataGibbs$G[7],
          dataGibbs$A[8]*log(t[match(c((dataGibbs$Max_Temp[7]+1):maxTemp), T)]) +
            dataGibbs$B[8]*t[match(c((dataGibbs$Max_Temp[7]+1):maxTemp), T)] +
            (dataGibbs$C[8]*t[match(c((dataGibbs$Max_Temp[7]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[8]*t[match(c((dataGibbs$Max_Temp[7]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[8]/(2*t[match(c((dataGibbs$Max_Temp[7]+1):maxTemp), T)]^2) +
            dataGibbs$G[8])

S_Al <- c(dataGibbs$A[9]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[9]), T)]) +
            dataGibbs$B[9]*t[match(c(lowTemp:dataGibbs$Max_Temp[9]), T)] +
            (dataGibbs$C[9]*t[match(c(lowTemp:dataGibbs$Max_Temp[9]), T)]^2)/2 +
            (dataGibbs$D[9]*t[match(c(lowTemp:dataGibbs$Max_Temp[9]), T)]^3)/3 -
            dataGibbs$E[9]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[9]), T)]^2) +
            dataGibbs$G[9],
          dataGibbs$A[10]*log(t[match(c((dataGibbs$Max_Temp[9]+1):maxTemp), T)]) +
            dataGibbs$B[10]*t[match(c((dataGibbs$Max_Temp[9]+1):maxTemp), T)] +
            (dataGibbs$C[10]*t[match(c((dataGibbs$Max_Temp[9]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[10]*t[match(c((dataGibbs$Max_Temp[9]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[10]/(2*t[match(c((dataGibbs$Max_Temp[9]+1):maxTemp), T)]^2) +
            dataGibbs$G[10])

S_Al2O3_alpha <- c(dataGibbs$A[11]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[11]), T)]) +
            dataGibbs$B[11]*t[match(c(lowTemp:dataGibbs$Max_Temp[11]), T)] +
            (dataGibbs$C[11]*t[match(c(lowTemp:dataGibbs$Max_Temp[11]), T)]^2)/2 +
            (dataGibbs$D[11]*t[match(c(lowTemp:dataGibbs$Max_Temp[11]), T)]^3)/3 -
            dataGibbs$E[11]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[11]), T)]^2) +
            dataGibbs$G[11],
          dataGibbs$A[15]*log(t[match(c((dataGibbs$Max_Temp[11]+1):maxTemp), T)]) +
            dataGibbs$B[15]*t[match(c((dataGibbs$Max_Temp[11]+1):maxTemp), T)] +
            (dataGibbs$C[15]*t[match(c((dataGibbs$Max_Temp[11]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[15]*t[match(c((dataGibbs$Max_Temp[11]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[15]/(2*t[match(c((dataGibbs$Max_Temp[11]+1):maxTemp), T)]^2) +
            dataGibbs$G[15])

S_Al2O3_gamma <- c(dataGibbs$A[12]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[12]), T)]) +
            dataGibbs$B[12]*t[match(c(lowTemp:dataGibbs$Max_Temp[12]), T)] +
            (dataGibbs$C[12]*t[match(c(lowTemp:dataGibbs$Max_Temp[12]), T)]^2)/2 +
            (dataGibbs$D[12]*t[match(c(lowTemp:dataGibbs$Max_Temp[12]), T)]^3)/3 -
            dataGibbs$E[12]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[12]), T)]^2) +
            dataGibbs$G[12],
          dataGibbs$A[15]*log(t[match(c((dataGibbs$Max_Temp[12]+1):maxTemp), T)]) +
            dataGibbs$B[15]*t[match(c((dataGibbs$Max_Temp[12]+1):maxTemp), T)] +
            (dataGibbs$C[15]*t[match(c((dataGibbs$Max_Temp[12]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[15]*t[match(c((dataGibbs$Max_Temp[12]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[15]/(2*t[match(c((dataGibbs$Max_Temp[12]+1):maxTemp), T)]^2) +
            dataGibbs$G[15])

S_Al2O3_delta <- c(dataGibbs$A[13]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[13]), T)]) +
            dataGibbs$B[13]*t[match(c(lowTemp:dataGibbs$Max_Temp[13]), T)] +
            (dataGibbs$C[13]*t[match(c(lowTemp:dataGibbs$Max_Temp[13]), T)]^2)/2 +
            (dataGibbs$D[13]*t[match(c(lowTemp:dataGibbs$Max_Temp[13]), T)]^3)/3 -
            dataGibbs$E[13]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[13]), T)]^2) +
            dataGibbs$G[13],
          dataGibbs$A[15]*log(t[match(c((dataGibbs$Max_Temp[13]+1):maxTemp), T)]) +
            dataGibbs$B[15]*t[match(c((dataGibbs$Max_Temp[13]+1):maxTemp), T)] +
            (dataGibbs$C[15]*t[match(c((dataGibbs$Max_Temp[13]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[15]*t[match(c((dataGibbs$Max_Temp[13]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[15]/(2*t[match(c((dataGibbs$Max_Temp[13]+1):maxTemp), T)]^2) +
            dataGibbs$G[15])

S_Al2O3_kappa <- c(dataGibbs$A[14]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[14]), T)]) +
            dataGibbs$B[14]*t[match(c(lowTemp:dataGibbs$Max_Temp[14]), T)] +
            (dataGibbs$C[14]*t[match(c(lowTemp:dataGibbs$Max_Temp[14]), T)]^2)/2 +
            (dataGibbs$D[14]*t[match(c(lowTemp:dataGibbs$Max_Temp[14]), T)]^3)/3 -
            dataGibbs$E[14]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[14]), T)]^2) +
            dataGibbs$G[14],
          dataGibbs$A[15]*log(t[match(c((dataGibbs$Max_Temp[14]+1):maxTemp), T)]) +
            dataGibbs$B[15]*t[match(c((dataGibbs$Max_Temp[14]+1):maxTemp), T)] +
            (dataGibbs$C[15]*t[match(c((dataGibbs$Max_Temp[14]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[15]*t[match(c((dataGibbs$Max_Temp[14]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[15]/(2*t[match(c((dataGibbs$Max_Temp[14]+1):maxTemp), T)]^2) +
            dataGibbs$G[15])

S_V <- c(dataGibbs$A[16]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[16]), T)]) +
            dataGibbs$B[16]*t[match(c(lowTemp:dataGibbs$Max_Temp[16]), T)] +
            (dataGibbs$C[16]*t[match(c(lowTemp:dataGibbs$Max_Temp[16]), T)]^2)/2 +
            (dataGibbs$D[16]*t[match(c(lowTemp:dataGibbs$Max_Temp[16]), T)]^3)/3 -
            dataGibbs$E[16]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[16]), T)]^2) +
            dataGibbs$G[16],
          dataGibbs$A[17]*log(t[match(c((dataGibbs$Max_Temp[16]+1):maxTemp), T)]) +
            dataGibbs$B[17]*t[match(c((dataGibbs$Max_Temp[16]+1):maxTemp), T)] +
            (dataGibbs$C[17]*t[match(c((dataGibbs$Max_Temp[16]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[17]*t[match(c((dataGibbs$Max_Temp[16]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[17]/(2*t[match(c((dataGibbs$Max_Temp[16]+1):maxTemp), T)]^2) +
            dataGibbs$G[17])

S_VO <- c(dataGibbs$A[18]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[18]), T)]) +
            dataGibbs$B[18]*t[match(c(lowTemp:dataGibbs$Max_Temp[18]), T)] +
            (dataGibbs$C[18]*t[match(c(lowTemp:dataGibbs$Max_Temp[18]), T)]^2)/2 +
            (dataGibbs$D[18]*t[match(c(lowTemp:dataGibbs$Max_Temp[18]), T)]^3)/3 -
            dataGibbs$E[18]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[18]), T)]^2) +
            dataGibbs$G[18],
          dataGibbs$A[19]*log(t[match(c((dataGibbs$Max_Temp[18]+1):maxTemp), T)]) +
            dataGibbs$B[19]*t[match(c((dataGibbs$Max_Temp[18]+1):maxTemp), T)] +
            (dataGibbs$C[19]*t[match(c((dataGibbs$Max_Temp[18]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[19]*t[match(c((dataGibbs$Max_Temp[18]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[19]/(2*t[match(c((dataGibbs$Max_Temp[18]+1):maxTemp), T)]^2) +
            dataGibbs$G[19])

S_V2O3 <- c(dataGibbs$A[20]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[20]), T)]) +
            dataGibbs$B[20]*t[match(c(lowTemp:dataGibbs$Max_Temp[20]), T)] +
            (dataGibbs$C[20]*t[match(c(lowTemp:dataGibbs$Max_Temp[20]), T)]^2)/2 +
            (dataGibbs$D[20]*t[match(c(lowTemp:dataGibbs$Max_Temp[20]), T)]^3)/3 -
            dataGibbs$E[20]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[20]), T)]^2) +
            dataGibbs$G[20],
          dataGibbs$A[21]*log(t[match(c((dataGibbs$Max_Temp[20]+1):maxTemp), T)]) +
            dataGibbs$B[21]*t[match(c((dataGibbs$Max_Temp[20]+1):maxTemp), T)] +
            (dataGibbs$C[21]*t[match(c((dataGibbs$Max_Temp[20]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[21]*t[match(c((dataGibbs$Max_Temp[20]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[21]/(2*t[match(c((dataGibbs$Max_Temp[20]+1):maxTemp), T)]^2) +
            dataGibbs$G[21])

S_V2O5 <- c(dataGibbs$A[22]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[22]), T)]) +
            dataGibbs$B[22]*t[match(c(lowTemp:dataGibbs$Max_Temp[22]), T)] +
            (dataGibbs$C[22]*t[match(c(lowTemp:dataGibbs$Max_Temp[22]), T)]^2)/2 +
            (dataGibbs$D[22]*t[match(c(lowTemp:dataGibbs$Max_Temp[22]), T)]^3)/3 -
            dataGibbs$E[22]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[22]), T)]^2) +
            dataGibbs$G[22],
          dataGibbs$A[23]*log(t[match(c((dataGibbs$Max_Temp[22]+1):maxTemp), T)]) +
            dataGibbs$B[23]*t[match(c((dataGibbs$Max_Temp[22]+1):maxTemp), T)] +
            (dataGibbs$C[23]*t[match(c((dataGibbs$Max_Temp[22]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[23]*t[match(c((dataGibbs$Max_Temp[22]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[23]/(2*t[match(c((dataGibbs$Max_Temp[22]+1):maxTemp), T)]^2) +
            dataGibbs$G[23])

S_Ti_alpha <- c(dataGibbs$A[24]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[24]), T)]) +
            dataGibbs$B[24]*t[match(c(lowTemp:dataGibbs$Max_Temp[24]), T)] +
            (dataGibbs$C[24]*t[match(c(lowTemp:dataGibbs$Max_Temp[24]), T)]^2)/2 +
            (dataGibbs$D[24]*t[match(c(lowTemp:dataGibbs$Max_Temp[24]), T)]^3)/3 -
            dataGibbs$E[24]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[24]), T)]^2) +
            dataGibbs$G[24],
          dataGibbs$A[25]*log(t[match(c((dataGibbs$Max_Temp[24]+1):dataGibbs$Max_Temp[25]), T)]) +
            dataGibbs$B[25]*t[match(c((dataGibbs$Max_Temp[24]+1):dataGibbs$Max_Temp[25]), T)] +
            (dataGibbs$C[25]*t[match(c((dataGibbs$Max_Temp[24]+1):dataGibbs$Max_Temp[25]), T)]^2)/2 +
            (dataGibbs$D[25]*t[match(c((dataGibbs$Max_Temp[24]+1):dataGibbs$Max_Temp[25]), T)]^3)/3 -
            dataGibbs$E[25]/(2*t[match(c((dataGibbs$Max_Temp[24]+1):dataGibbs$Max_Temp[25]), T)]^2) +
            dataGibbs$G[25],
          dataGibbs$A[27]*log(t[match(c((dataGibbs$Max_Temp[25]+1):maxTemp), T)]) +
            dataGibbs$B[27]*t[match(c((dataGibbs$Max_Temp[25]+1):maxTemp), T)] +
            (dataGibbs$C[27]*t[match(c((dataGibbs$Max_Temp[25]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[27]*t[match(c((dataGibbs$Max_Temp[25]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[27]/(2*t[match(c((dataGibbs$Max_Temp[25]+1):maxTemp), T)]^2) +
            dataGibbs$G[27])

S_Ti_beta <- c(dataGibbs$A[26]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[26]), T)]) +
            dataGibbs$B[26]*t[match(c(lowTemp:dataGibbs$Max_Temp[26]), T)] +
            (dataGibbs$C[26]*t[match(c(lowTemp:dataGibbs$Max_Temp[26]), T)]^2)/2 +
            (dataGibbs$D[26]*t[match(c(lowTemp:dataGibbs$Max_Temp[26]), T)]^3)/3 -
            dataGibbs$E[26]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[26]), T)]^2) +
            dataGibbs$G[26],
          dataGibbs$A[27]*log(t[match(c((dataGibbs$Max_Temp[26]+1):maxTemp), T)]) +
            dataGibbs$B[27]*t[match(c((dataGibbs$Max_Temp[26]+1):maxTemp), T)] +
            (dataGibbs$C[27]*t[match(c((dataGibbs$Max_Temp[26]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[27]*t[match(c((dataGibbs$Max_Temp[26]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[27]/(2*t[match(c((dataGibbs$Max_Temp[26]+1):maxTemp), T)]^2) +
            dataGibbs$G[27])

S_Ti2_O3 <- c(dataGibbs$A[28]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[28]), T)]) +
            dataGibbs$B[28]*t[match(c(lowTemp:dataGibbs$Max_Temp[28]), T)] +
            (dataGibbs$C[28]*t[match(c(lowTemp:dataGibbs$Max_Temp[28]), T)]^2)/2 +
            (dataGibbs$D[28]*t[match(c(lowTemp:dataGibbs$Max_Temp[28]), T)]^3)/3 -
            dataGibbs$E[28]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[28]), T)]^2) +
            dataGibbs$G[28],
          dataGibbs$A[29]*log(t[match(c((dataGibbs$Max_Temp[28]+1):dataGibbs$Max_Temp[29]), T)]) +
            dataGibbs$B[29]*t[match(c((dataGibbs$Max_Temp[28]+1):dataGibbs$Max_Temp[29]), T)] +
            (dataGibbs$C[29]*t[match(c((dataGibbs$Max_Temp[28]+1):dataGibbs$Max_Temp[29]), T)]^2)/2 +
            (dataGibbs$D[29]*t[match(c((dataGibbs$Max_Temp[28]+1):dataGibbs$Max_Temp[29]), T)]^3)/3 -
            dataGibbs$E[29]/(2*t[match(c((dataGibbs$Max_Temp[28]+1):dataGibbs$Max_Temp[29]), T)]^2) +
            dataGibbs$G[29],
          dataGibbs$A[30]*log(t[match(c((dataGibbs$Max_Temp[29]+1):maxTemp), T)]) +
            dataGibbs$B[30]*t[match(c((dataGibbs$Max_Temp[29]+1):maxTemp), T)] +
            (dataGibbs$C[30]*t[match(c((dataGibbs$Max_Temp[29]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[30]*t[match(c((dataGibbs$Max_Temp[29]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[30]/(2*t[match(c((dataGibbs$Max_Temp[29]+1):maxTemp), T)]^2) +
            dataGibbs$G[30])

S_TiO_alpha <- c(dataGibbs$A[31]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[31]), T)]) +
            dataGibbs$B[31]*t[match(c(lowTemp:dataGibbs$Max_Temp[31]), T)] +
            (dataGibbs$C[31]*t[match(c(lowTemp:dataGibbs$Max_Temp[31]), T)]^2)/2 +
            (dataGibbs$D[31]*t[match(c(lowTemp:dataGibbs$Max_Temp[31]), T)]^3)/3 -
            dataGibbs$E[31]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[31]), T)]^2) +
            dataGibbs$G[31],
          dataGibbs$A[33]*log(t[match(c((dataGibbs$Max_Temp[31]+1):maxTemp), T)]) +
            dataGibbs$B[33]*t[match(c((dataGibbs$Max_Temp[31]+1):maxTemp), T)] +
            (dataGibbs$C[33]*t[match(c((dataGibbs$Max_Temp[31]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[33]*t[match(c((dataGibbs$Max_Temp[31]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[33]/(2*t[match(c((dataGibbs$Max_Temp[31]+1):maxTemp), T)]^2) +
            dataGibbs$G[33])

S_TiO_beta <- c(dataGibbs$A[32]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[32]), T)]) +
            dataGibbs$B[32]*t[match(c(lowTemp:dataGibbs$Max_Temp[32]), T)] +
            (dataGibbs$C[32]*t[match(c(lowTemp:dataGibbs$Max_Temp[32]), T)]^2)/2 +
            (dataGibbs$D[32]*t[match(c(lowTemp:dataGibbs$Max_Temp[32]), T)]^3)/3 -
            dataGibbs$E[32]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[32]), T)]^2) +
            dataGibbs$G[32],
          dataGibbs$A[33]*log(t[match(c((dataGibbs$Max_Temp[32]+1):maxTemp), T)]) +
            dataGibbs$B[33]*t[match(c((dataGibbs$Max_Temp[32]+1):maxTemp), T)] +
            (dataGibbs$C[33]*t[match(c((dataGibbs$Max_Temp[32]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[33]*t[match(c((dataGibbs$Max_Temp[32]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[33]/(2*t[match(c((dataGibbs$Max_Temp[32]+1):maxTemp), T)]^2) +
            dataGibbs$G[33])

S_Cu <- c(dataGibbs$A[34]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[34]), T)]) +
            dataGibbs$B[34]*t[match(c(lowTemp:dataGibbs$Max_Temp[34]), T)] +
            (dataGibbs$C[34]*t[match(c(lowTemp:dataGibbs$Max_Temp[34]), T)]^2)/2 +
            (dataGibbs$D[34]*t[match(c(lowTemp:dataGibbs$Max_Temp[34]), T)]^3)/3 -
            dataGibbs$E[34]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[34]), T)]^2) +
            dataGibbs$G[34],
          dataGibbs$A[35]*log(t[match(c((dataGibbs$Max_Temp[34]+1):maxTemp), T)]) +
            dataGibbs$B[35]*t[match(c((dataGibbs$Max_Temp[34]+1):maxTemp), T)] +
            (dataGibbs$C[35]*t[match(c((dataGibbs$Max_Temp[34]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[35]*t[match(c((dataGibbs$Max_Temp[34]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[35]/(2*t[match(c((dataGibbs$Max_Temp[34]+1):maxTemp), T)]^2) +
            dataGibbs$G[35])

S_Cu2O <- c(dataGibbs$A[36]*log(t[match(c(lowTemp:dataGibbs$Max_Temp[36]), T)]) +
            dataGibbs$B[36]*t[match(c(lowTemp:dataGibbs$Max_Temp[36]), T)] +
            (dataGibbs$C[36]*t[match(c(lowTemp:dataGibbs$Max_Temp[36]), T)]^2)/2 +
            (dataGibbs$D[36]*t[match(c(lowTemp:dataGibbs$Max_Temp[36]), T)]^3)/3 -
            dataGibbs$E[36]/(2*t[match(c(lowTemp:dataGibbs$Max_Temp[36]), T)]^2) +
            dataGibbs$G[36],
          dataGibbs$A[37]*log(t[match(c((dataGibbs$Max_Temp[36]+1):dataGibbs$Max_Temp[37]), T)]) +
            dataGibbs$B[37]*t[match(c((dataGibbs$Max_Temp[36]+1):dataGibbs$Max_Temp[37]), T)] +
            (dataGibbs$C[37]*t[match(c((dataGibbs$Max_Temp[36]+1):dataGibbs$Max_Temp[37]), T)]^2)/2 +
            (dataGibbs$D[37]*t[match(c((dataGibbs$Max_Temp[36]+1):dataGibbs$Max_Temp[37]), T)]^3)/3 -
            dataGibbs$E[37]/(2*t[match(c((dataGibbs$Max_Temp[36]+1):dataGibbs$Max_Temp[37]), T)]^2) +
            dataGibbs$G[37],
          dataGibbs$A[38]*log(t[match(c((dataGibbs$Max_Temp[37]+1):maxTemp), T)]) +
            dataGibbs$B[38]*t[match(c((dataGibbs$Max_Temp[37]+1):maxTemp), T)] +
            (dataGibbs$C[38]*t[match(c((dataGibbs$Max_Temp[37]+1):maxTemp), T)]^2)/2 +
            (dataGibbs$D[38]*t[match(c((dataGibbs$Max_Temp[37]+1):maxTemp), T)]^3)/3 -
            dataGibbs$E[38]/(2*t[match(c((dataGibbs$Max_Temp[37]+1):maxTemp), T)]^2) +
            dataGibbs$G[38])

S_CuO <- c(dataGibbs$A[39]*log(t[match(c(lowTemp:maxTemp), T)]) +
            dataGibbs$B[39]*t[match(c(lowTemp:maxTemp), T)] +
            (dataGibbs$C[39]*t[match(c(lowTemp:maxTemp), T)]^2)/2 +
            (dataGibbs$D[39]*t[match(c(lowTemp:maxTemp), T)]^3)/3 -
            dataGibbs$E[39]/(2*t[match(c(lowTemp:maxTemp), T)]^2) +
            dataGibbs$G[39])
```

###Caluculate Gibbs Free Energy of each chemical
```{r}
O2 <- H_O2-t*S_O2

Si <- H_Si-t*S_Si

SiO2 <- H_SiO2-t*S_SiO2

Al <- H_Al-t*S_Al

Al2O3_alpha <- H_Al2O3_alpha-t*S_Al2O3_alpha

Al2O3_delta <- H_Al2O3_delta-t*S_Al2O3_delta

Al2O3_gamma <- H_Al2O3_gamma-t*S_Al2O3_gamma

Al2O3_kappa <- H_Al2O3_kappa-t*S_Al2O3_kappa

V <- H_V-t*S_V

VO <- H_VO-t*S_VO

V2O3 <- H_V2O3-t*S_V2O3

V2O5 <- H_V2O5-t*S_V2O5

Ti_alpha <- H_Ti_alpha-t*S_Ti_alpha

Ti_beta <- H_Ti_beta-t*S_Ti_beta

Ti2O3 <- H_Ti2O3-t*S_Ti2_O3

TiO_alpha <- H_TiO_alpha-t*S_TiO_alpha

TiO_beta <- H_TiO_beta-t*S_TiO_beta

Cu <- H_Cu-t*S_Cu

Cu2O <- H_Cu2O-t*S_Cu2O

CuO <- H_CuO-t*S_CuO
```

### Assemble data frames
```{r}
H <- data.frame(H_O2, H_Si, H_SiO2, H_Al, H_Al2O3_alpha, H_Al2O3_delta, H_Al2O3_gamma, H_Al2O3_kappa,
                H_V, H_VO, H_V2O3, H_V2O5, H_Ti_alpha, H_Ti_beta, H_Ti2O3, H_TiO_alpha, H_TiO_beta,
                H_Cu, H_Cu2O, H_CuO)

S <- data.frame(S_O2, S_Si, S_SiO2, S_Al, S_Al2O3_alpha, S_Al2O3_delta, S_Al2O3_gamma, S_Al2O3_kappa,
                S_V, S_VO, S_V2O3, S_V2O5, S_Ti_alpha, S_Ti_beta, S_Ti2_O3, S_TiO_alpha, S_TiO_beta,
                S_Cu, S_Cu2O, S_CuO)

GibbsFreeEnergy <- data.frame(O2, Si, SiO2, Al, Al2O3_alpha, Al2O3_delta, Al2O3_gamma, Al2O3_kappa,
                              V, VO, V2O3, V2O5, Ti_alpha, Ti_beta, Ti2O3, TiO_alpha, TiO_beta,
                              Cu, Cu2O, CuO)

write.csv(H, 'H.csv')
write.csv(S, 'S.csv')
write.csv(GibbsFreeEnergy, 'GibbsFreeEnergy.csv')
                              
```

### Reactions
```{r}
Al2O3_alpha_react <- (2*Al2O3_alpha + 3*Si) - (3*SiO2 + 4*Al)
Al2O3_delta_react <- (2*Al2O3_delta + 3*Si) - (3*SiO2 + 4*Al)
Al2O3_gamma_react <- (2*Al2O3_gamma + 3*Si) - (3*SiO2 + 4*Al)
Al2O3_kappa_react <- (2*Al2O3_kappa + 3*Si) - (3*SiO2 + 4*Al)
VO_react <- (2*VO + Si) - (SiO2 + 2*V)
V2O3_react <- (2*V2O3 + 3*Si) - (3*SiO2 + 4*V)
V2O5_react <- (2*V2O5 + 5*Si) - (5*SiO2 + 4*V)
Ti2O3_a_react <- (2*Ti2O3 + 3*Si) - (3*SiO2 + 4*Ti_alpha)
Ti2O3_b_react <- (2*Ti2O3 + 3*Si) - (3*SiO2 + 4*Ti_beta)
TiO_aa_react <- (2*TiO_alpha + Si) - (SiO2 + 2*Ti_alpha)
TiO_ab_react <- (2*TiO_beta + Si) - (SiO2 + 2*Ti_alpha)
TiO_ba_react <- (2*TiO_alpha + Si) - (SiO2 + 2*Ti_beta)
TiO_bb_react <- (2*TiO_beta + Si) - (SiO2 + 2*Ti_beta)
Cu2O_react <- (2*Cu2O + Si) - (SiO2 + 4*Cu)
CuO_react <- (2*CuO + Si) - (SiO2 + 2*Cu)

```

### Assemble Gibbs Free Energy of Reaction data frame
```{r}
GibbsFreeEnergy_react <- data.frame(Al2O3_alpha_react, Al2O3_delta_react, Al2O3_gamma_react, Al2O3_kappa_react,
                                    VO_react, V2O3_react, V2O5_react, Ti2O3_a_react, Ti2O3_b_react,
                                    TiO_aa_react, TiO_ab_react, TiO_ba_react, TiO_bb_react,
                                    Cu2O_react, CuO_react)

write.csv(GibbsFreeEnergy_react, 'GibbsFreeEnergy_react.csv')
```

### Plots
```{r}
ggplot(data = GibbsFreeEnergy_react) + 
  geom_line(aes(x = T, y = Al2O3_alpha_react, color = 'Al2O3 alpha')) + 
        geom_line(aes(x = T, y = Al2O3_delta_react, color = 'Al2O3 delta')) + 
        geom_line(aes(x = T, y = Al2O3_gamma_react, color = 'Al2O3 gamma')) +
        geom_line(aes(x = T, y = Al2O3_kappa_react, color = 'Al2O3 kappa')) +
  ggtitle('Aluminum Reaction') + 
  labs(x = "Temperature (K)",
       y = "Gibbs Free Energy (kJ/mol)",
        color = "Oxide") 
```

```{r}
ggplot(data = GibbsFreeEnergy_react) + 
  geom_line(aes(x = T, y = VO_react, color = 'VO')) + 
        geom_line(aes(x = T, y = V2O3_react, color = 'V2O3')) + 
        geom_line(aes(x = T, y = V2O5_react, color = 'V2O5')) +
  ggtitle('Vanadium Reaction') + 
  labs(x = "Temperature (K)",
       y = "Gibbs Free Energy (kJ/mol)",
        color = "Oxide") 
```

```{r}
ggplot(data = GibbsFreeEnergy_react) + 
  geom_line(aes(x = T, y = Ti2O3_a_react, color = 'Ti2O3 from Ti alpha')) +
        geom_line(aes(x = T, y = Ti2O3_b_react, color = 'Ti2O3 from Ti beta')) +
        geom_line(aes(x = T, y = TiO_aa_react, color = 'TiO alpha from Ti alpha')) +
        geom_line(aes(x = T, y = TiO_ab_react, color = 'TiO alpha from Ti beta')) +
        geom_line(aes(x = T, y = TiO_ba_react, color = 'TiO beta from Ti alpha')) +
        geom_line(aes(x = T, y = TiO_bb_react, color = 'TiO beta from Ti beta')) +
  ggtitle('Titanium Reaction') + 
  labs(x = "Temperature (K)",
       y = "Gibbs Free Energy (kJ/mol)",
        color = "Oxide")
```

```{r}
ggplot(data = GibbsFreeEnergy_react[1:1707,]) + 
  geom_line(aes(x = T[1:1707], y = Cu2O_react, color = 'Cu2O')) + 
        geom_line(aes(x = T[1:1707], y = CuO_react, color = 'CuO')) + 
  ggtitle('Copper Reaction') + 
  labs(x = "Temperature (K)",
       y = "Gibbs Free Energy (kJ/mol)",
        color = "Oxide") 
```


